ODGI: scalable tools for pangenome graphs

### 2021-06-02 manuscript/main.tex
Fix table

@@

    %TODO to repeat on a bigger machine to avoid vg crashing
    \begin{table}[th]
      \processtable{\small
        Example of performance improvement between
        \cmd{odgi} and \cmd{vg}~\citep{vgtools} equivalent commands with output file
        sizes. The centromere region was extracted from CHR 6 of the
        HPRC year one assembly, i.e., 88~haploid, phased
        human genome assemblies from 44~individuals plus the chm13
        cell line and GRCh38 reference genomes stored in 4.3GB~GFA
        format\citep{GFA}.
        %
        First GFS was converted from GFA to \odgi\ and \vg\
        formats, respectively.  \odgi's path implementation can
        process paths in parallel, outperforming \vg. For the
        same reason \cmd{odgi extract} is $20\times$ faster than
        \cmd{vg chunk} extracting a portion from the full
        graph. \FIXME: vg never finished.
        %
        All timings were performed on a server class machine
        on SSD MODEL with X GB of RAM and 48 CPU cores (Y x 12 core
        AMD Opteron) Processor MODEL @ 3.3 GHz with 8MB L2
        Cache.\FIXME
        % \vspace{0.5in}
        \label{tab:02}}
                   {
                     % \resizebox{.8\textwidth}{!}{
            \begin{tabular*}{.5\textwidth}{@{}lllll@{}}
                \toprule Operation & Tool & Runtime (mm:ss) & Memory (GB) & Output size (GB)    \\
                \midrule
                Format conversion                           &       &       &                   \\
                                    & \cmd{odgi build}      & 1:35  & 10.39 & 5.4               \\
                                    & \cmd{vg convert}      & 8:14  & 28.43 & 6.1               \\
                Subgraph extraction                         &       &       &                   \\
                                    & \cmd{odgi extract}    & 1:15  & 9.43  & 2.7               \\
                                    & \cmd{vg chunk}        & 21:09 & 59.33 & 1.7               \\
                \botrule
            \end{tabular*}} %}

@@

    \textit{Conflict of Interest}: none declared.
    % \vspace*{+12pt}

>>>>

        %TODO to repeat on a bigger machine to avoid vg crashing
    \begin{table}[h!]
        \caption{ Example of performance improvement between
            \cmd{odgi} and \cmd{vg}~\citep{vgtools} equivalent
            commands with output file sizes. The centromere region was
            extracted from CHR 6 of the HPRC year one assembly, i.e.,
            88~haploid, phased human genome assemblies from
            44~individuals plus the chm13 cell line and GRCh38
            reference genomes stored in 4.3GB~GFA format\citep{GFA}.
            %
            First GFS was converted from GFA to \odgi\ and
            \vg\ formats, respectively.  \odgi's path implementation
            can process paths in parallel, outperforming \vg. For the
            same reason \cmd{odgi extract} is $20\times$ faster than
            \cmd{vg chunk} extracting a portion from the full
            graph. \FIXME: vg never finished.
            %
            All timings were performed on a server class machine
            on SSD MODEL with X GB of RAM and 48 CPU cores (Y x 12 core
        AMD Opteron) Processor MODEL @ 3.3 GHz with 8MB L2
        Cache.\FIXME}
        \begin{tabular}{{@{}lllll@{}}}
          \toprule
          Operation & Command & Runtime & Memory  & File size     \\
                    &      & (mm:ss) & (GB) & (GB)           \\
          \midrule
          Covert GFA to native format                         &       &       &                   \\
          & \cmd{odgi build}      & 1:35  & 10.39 & 5.4               \\
          & \cmd{vg convert}      & 8:14  & 28.43 & 6.1               \\
          Extract subgraph                         &       &       &                   \\
          & \cmd{odgi extract}    & 1:15  & 9.43  & 2.7               \\
          & \cmd{vg chunk}        & 21:09 & 59.33 & 1.7               \\
          \botrule
        \end{tabular}
        \label{tab:02}

@@

@@

    \textit{Conflict of Interest}: none declared.
    \vspace*{+24pt}
